---
title: "Raw Data"
format: html
editor: visual
---

```{r load data, message = FALSE, warning = FALSE, include = FALSE}
library(tidyverse)
library(leaflet)
library(htmlwidgets)
library(htmltools)
library(crosstalk)
library(bslib)
library(bsicons)
library(summarywidget)
library(reactable)
```

```{r}
#| echo: false
#| output: false

asop_raw <- read_csv("Suppl material 2/Suppl material 2.csv")


#READ DISTRBUTION DATA
asop <- read.csv("asopinae_v_1_0.csv", sep = ",")
asop <- asop %>%
  na.omit(asop) 
colnames(asop) <- c("Genus", "Species","Local_Label", "X_Longitude", "Y_Latitude", "Refs", "Country", "Continent", "Realm", "Country_Level_Record")

asop$X_Longitude <- as.numeric(asop$X_Longitude) 
asop$Y_Latitude <- as.numeric(asop$Y_Latitude)

row.names(asop) <- NULL

shared_asop <- SharedData$new(asop, group = "Asop")

shared_asop_raw <- SharedData$new(asop_raw, group = "Asop")

#share_species <- asop %>%
 # select(Species) %>%
#  unique() %>%
#  SharedData$new(group = "Asop")
```

This is the current database of "Asopinae of the World". Here, you can look at the raw data that originated this work, and the processed data used for the Distribution Map and analysis. 

We emphasize that ***some records are georeferenced only according to the country reported for the species***, as well as records that are the only ones known for a given species in a country.

## Raw data - 5831 records

```{r}
#| echo: false

bscols(
  value_box(
    title = "Records",
    value = summarywidget(shared_asop_raw),
    showcase = bsicons::bs_icon("search"),
    theme = value_box_theme(bg = "#2f4538", fg = "#F3EEEA"),
    width = 0.1
  )
  )
  

```

```{r}
#| echo: false


library(fontawesome)

htmltools::browsable(
    tagList(
      tags$button(
        tagList(fontawesome::fa("download"), "Download as CSV"),
        onclick = "Reactable.downloadDataCSV('asop_table_raw','Suppl material 2/Suppl material 2.csv')"
      ),
    reactable(shared_asop_raw,
              defaultColDef = colDef(
                  align = "left",
                  headerStyle = list(background = "#f7f7f8", fontSize = "11px"),  
                  style = list(fontSize = "11px") 
                ),
              columns = list(
            Genus = colDef(width = 60),
            Subgenus = colDef(width = 60),
            Species = colDef(width = 60),
            Author = colDef(width = 60),
            Local_Label = colDef(width = 100),
            X_Longitude = colDef(width = 60),
            Y_Latitude = colDef(width = 60),
            Refs = colDef(width = 80)
          ),
              elementId = 'asop_table',
              highlight = TRUE,
              pagination = FALSE,
              height = 1000,
              width = "100%",
              style = list(fontSize = "10px"))
  )
)
```


## Processed data - 5030 records

``` {r}
#| echo: false

bscols(
  value_box(
    title = "Records",
    value = summarywidget(shared_asop),
    showcase = bsicons::bs_icon("search"),
    theme = value_box_theme(bg = "#2f4538", fg = "#F3EEEA"),
    width = 0.1
  )
)

```


``` {r}
htmltools::browsable(
    tagList(
      tags$button(
        tagList(fontawesome::fa("download"), "Download as CSV"),
        onclick = "Reactable.downloadDataCSV('asop_table','asopinae_v_1_0.csv')"
      ),
    reactable(shared_asop,
              defaultColDef = colDef(
                  align = "left",
                  headerStyle = list(background = "#f7f7f8", fontSize = "11px"),  
                  style = list(fontSize = "11px") 
                ),
              columns = list(
            Genus = colDef(width = 50),
            Species = colDef(width = 80),
            Local_Label = colDef(width = 100),
            X_Longitude = colDef(width = 60),
            Y_Latitude = colDef(width = 60),
            Refs = colDef(width = 80),
            Country = colDef(width = 80),
            Continent = colDef(width = 80),
            Realm = colDef(width = 100),
            Country_Level_Record = colDef(width = 150)
          ),
              elementId = 'asop_table',
              highlight = TRUE,
              pagination = FALSE,
              height = 1000,
              width = "100%",
              style = list(fontSize = "10px"))
  )
)
  

```

